---

author: "jieun"
output: html_document
---

# version history 

```{r global_options, include=FALSE}
# set global chunk options...  
knitr::opts_chunk$set(comment     = "",
                      echo        = TRUE, 
                      comment     = FALSE,
                      warning     = FALSE, 
                      message     = FALSE)
```

```{r, echo=FALSE, results=FALSE, warning=FALSE, message=FALSE}
### ----- load package(s) ----- ###

library("tidyverse")    
library("forcats")
library("lubridate")    
library("readxl")
library("reshape2")
library("data.table")
library("dplyr")
library("readr")

library("psych")        
library("furniture")    
library("stargazer")    
library("pander")
library("writexl")

library("gridExtra")

panderOptions('digits', 3)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)
```

### Reading in the data files 
```{r}
# original demographic data from Craig
demo_data <- read_excel("Demo Data 20210124.xlsx")

# roster data at the beginning of the study 
roster_01 <- read_excel("roster_2020_09_07.xlsx")

# roster data at the end of the study 
roster_02 <- read_excel("finalrosters_allstudents_2021_04_25_updated.xlsx")

teacher_id <- read_excel("IES_school_teacher_ID_list.xlsx")

# performance level and scores
performance <- read.csv("Gr 7 milestones 20-21 De-ID.csv")
math <- read_excel("7th grade math final course grades 20-21.xlsx")
```

### replacing teacher name with teacher IDs
```{r}
#merging teacher id with school id 
roster_01$teacher_code <- paste(roster_01$`school ID`, roster_01$`Teacher Name`, roster_01$SectionNumber)

teacher_id$teacher_code <- paste(teacher_id$school_ID, teacher_id$`Teacher Name`, teacher_id$Section)

roster_01 <- roster_01 %>%
                    left_join(teacher_id, by = "teacher_code")

roster_01 <- roster_01 %>% select("student_number", "school ID", "SectionNumber", Student_ID, `Condition Assignment`, teacher_id, teacher_class)

col_order <- c("student_number", "Student_ID", "school ID", "teacher_id", "teacher_class", "SectionNumber", "Condition Assignment")

roster_01 <- roster_01[, col_order]
```


```{r}
roster_02$teacher_code <- paste(roster_02$`school ID`, roster_02$`Teacher Name`, roster_02$SectionNumber)

roster_02 <- roster_02 %>%
                    left_join(teacher_id, by = "teacher_code")

roster_02 <- roster_02 %>% select("student_number", "school ID", "SectionNumber", Student_ID, `Condition Assignment`, teacher_id, teacher_class, courseName)

col_order_2 <- c("student_number", "Student_ID", "school ID", "teacher_id", "teacher_class", "SectionNumber", "courseName", "Condition Assignment")

roster_02 <- roster_02[, col_order_2]
```

### change the type of the variables

```{r}
demo_data$student_number <- as.character(as.numeric(demo_data$student_number))
roster_01$student_number <- as.character(as.numeric(roster_01$student_number))
roster_02$student_number <- as.character(as.numeric(roster_02$student_number))
```


###### Gender information ######
```{r}
# gender data from the district 
DMS_gender <- read.csv("enrollmentStatus DMS.csv")
FVA_gender <- read.csv("enrollmentStatus FVA.csv")
LakMS_gender <- read.csv("enrollmentStatus LakMS.csv")
LibMS_gender <- read.csv("enrollmentStatus LibMS.csv")
LMMS_gender <- read.csv("enrollmentStatus LMMS.csv")
NFMS_gender <- read.csv("enrollmentStatus NFMS.csv")
OMS_gender <- read.csv("enrollmentStatus OMS.csv")
PGMS_gender <- read.csv("enrollmentStatus PGMS.csv")
RMS_gender <- read.csv("enrollmentStatus RMS.csv")
SFMS_gender <- read.csv("enrollmentStatus SFMS.csv")
VCMS_gender <- read.csv("enrollmentStatus VCMS.csv")
```

# cleaning the gender data file 
```{r}
# merging the data files 
gender_all <- rbind(DMS_gender, FVA_gender, LakMS_gender, LibMS_gender, LMMS_gender, NFMS_gender, OMS_gender, PGMS_gender, RMS_gender, SFMS_gender, VCMS_gender)

# drop the duplicates
gender <- gender_all %>% distinct(Number, .keep_all = TRUE)

# drop the unnecessary columns 
gender <- gender %>% select(Number, Gender)

# change the column name and the type 
names(gender)[names(gender) == "Number"] <- "student_number"
gender$student_number <- as.character(as.numeric(gender$student_number))
```


###### Ethnicity information ######
```{r}
DMS_eth <- read_excel("DMS 7th gr math roster 2.8.21 ethnicity.xlsx")
FVA_eth <- read_excel("FVA 7th gr math roster 2.8.21 ethnicity.xlsx")
LakMS_eth <- read_excel("LakMS 7th gr math roster 2.8.21 ethnicity.xlsx")
LibMS_eth <- read_excel("LibMS 7th gr math roster 2.8.21 ethnicity.xlsx")
LMMS_eth <- read_excel("LMMS 7th gr math roster 2.8.21 ethnicity.xlsx")
NFMS_eth <- read_excel("NFMS 7th gr math roster 2.8.21 ethnicity.xlsx")
OMS_eth <- read_excel("OMS 7th gr math roster 2.8.21 ethnicity.xlsx")
PGMS_eth <- read_excel("PGMS 7th gr math roster 2.8.21 ethnicity.xlsx")
RMS_eth <- read_excel("RMS 7th gr math roster 2.8.21 ethnicity.xlsx")
SFMS_eth <- read_excel("SFMS 7th gr math roster 2.8.21 ethnicity.xlsx")
VCMS_eth <- read_excel("VCMS 7th gr math roster 2.8.21 ethnicity.xlsx")
```

# cleaning the Ethnicity data file
```{r}
# merging the data files 
eth_all <- rbind(DMS_eth, FVA_eth, LakMS_eth, LibMS_eth, LMMS_eth, NFMS_eth, OMS_eth, PGMS_eth, RMS_eth, SFMS_eth, VCMS_eth)

# drop the duplicates
eth <- eth_all %>% distinct(student_studentNumber, .keep_all = TRUE)

# drop the unnecessary columns 
eth <- eth %>% select(student_studentNumber, student_raceEthnicity, student_hispanicEthnicity, student_raceEthnicityFed)

# change the column name and the type 
names(eth)[names(eth) == "student_studentNumber"] <- "student_number"
names(eth)[names(eth) == "student_raceEthnicity"] <- "raceEthnicity"
names(eth)[names(eth) == "student_hispanicEthnicity"] <- "hispanicEthnicity"
names(eth)[names(eth) == "student_raceEthnicityFed"] <- "raceEthnicityFed"
eth$student_number <- as.character(as.numeric(eth$student_number))
```


###### ADMADA information ######
```{r}
# demographic data from the district 
DMS <- read.csv("ADMADA 20-21 DMS De-ID.csv")
FVA <- read.csv("ADMADA 20-21 FVA De-ID.csv")
LakMS <- read.csv("ADMADA 20-21 LakMS De-ID.csv")
LibMS <- read.csv("ADMADA 20-21 LibMS De-ID.csv")
LMMS <- read.csv("ADMADA 20-21 LMMS De-ID.csv")
NFMS <- read.csv("ADMADA 20-21 NFMS De-ID.csv")
OMS <- read.csv("ADMADA 20-21 OMS De-ID.csv")
PGMS <- read.csv("ADMADA 20-21 PGMS De-ID.csv")
RMS <- read.csv("ADMADA 20-21 RMS De-ID.csv")
SFMS <- read.csv("ADMADA 20-21 SFMS De-ID.csv")
VCMS <- read.csv("ADMADA 20-21 VCMS De-ID.csv")
```

# cleaning the ADMADA data file 
```{r}
# merging the data files
ADMADA_all <- rbind(DMS, FVA, LakMS, LibMS, LMMS, NFMS, OMS, PGMS, RMS, SFMS, VCMS)

ADMADA_all <- ADMADA_all %>% mutate(base = case_when(
                      School %in% c("DeSana Middle School", "Lakeside Middle School", "Liberty Middle School", "Little Mill Middle School", "North Forsyth Middle School", "Otwell Middle School", "Piney Grove Middle School", "Riverwatch Middle School", "South Forsyth Middle School", "Vickery Creek Middle School") ~ "YES",
                      School == "Forsyth Virtual Academy" ~ "No"))
                      

ADMADA_all <- ADMADA_all[order(ADMADA_all$base),]
ADMADA <- ADMADA_all[!duplicated(ADMADA_all$Student.Number, fromLast = T), ]

# drop the unnecessary columns 
ADMADA <- ADMADA %>% select(-School, -Grade, -Student.Count, -Student.First.Name, -Calendar, -base)

# change the column name and the type 
names(ADMADA)[names(ADMADA) == "Student.Number"] <- "student_number"
names(ADMADA)[names(ADMADA) == "Absences.avg..Daily"] <- "Absences.avg.Daily7"
names(ADMADA)[names(ADMADA) == "Absent.Days"] <- "Absent.Days7"
names(ADMADA)[names(ADMADA) == "ADM"] <- "ADM7"
names(ADMADA)[names(ADMADA) == "Membership.Days"] <- "Membership.Days7"
names(ADMADA)[names(ADMADA) == "Percent.In.Attendance"] <- "Percent.In.Attendance7"
names(ADMADA)[names(ADMADA) == "Present.Days"] <- "Present.Days7"
names(ADMADA)[names(ADMADA) == "Unexcused.Days"] <- "Unexcused.Days7"

ADMADA$student_number <- as.character(as.numeric(ADMADA$student_number))
```


###### performance information ######
```{r}
performance <- performance %>% select(-School, -Level.Tested)
names(performance)[names(performance) == "Student.ID"] <- "student_number"
names(performance)[names(performance) == "Scale.Score"] <- "Scale.Score7"
names(performance)[names(performance) == "Performance.Level"] <- "Performance.Level7"
performance$student_number <- as.character(as.numeric(performance$student_number))
performance <- performance %>% distinct(student_number, .keep_all = TRUE)


math <- math %>% select(-"CRS#", -`Course name`)
names(math)[names(math) == "ST#"] <- "student_number"
math$student_number <- as.character(as.numeric(math$student_number))
```



### data merge 
```{r}
df <- roster_01 %>% full_join(roster_02, by = "student_number") %>%
                    full_join(gender, by = "student_number") %>%
                    full_join(eth, by = "student_number") %>%
                    full_join(demo_data, by = "student_number") %>%
                    full_join(ADMADA, by = "student_number") %>%
                    full_join(performance, by = "student_number") %>%
                    full_join(math, by = "student_number") 
```


### Reshaping the aggregated file 
```{r}
# Replace student_id_x with NA with the value from student_id_x
df$Student_ID.x <- ifelse(is.na(df$Student_ID.x), df$Student_ID.y, df$Student_ID.x)

df$'Condition Assignment.x' <- ifelse(is.na(df$'Condition Assignment.x'), df$'Condition Assignment.y', df$'Condition Assignment.x')

# dropping the duplicated column 
df <- df %>% select(-`Condition Assignment.y`, -Student_ID.y)
 

# changing the variable names 
df <- df %>%
  rename(
         student_id = Student_ID.x,
         initial_school_id = `school ID.x`,
         initial_teacher_id = teacher_id.x, 
         initial_teacher_class = teacher_class.x,
         initial_section_number = SectionNumber.x,
         condition_assignment = `Condition Assignment.x`,
         final_school_id = `school ID.y`,
         final_teacher_id = teacher_id.y,
         final_teacher_class = teacher_class.y,
         final_section_number = SectionNumber.y, 
         rdm_condition = CONDITION)
```


### Adding movement information 
```{r}
df <- df %>%
  mutate(movement = case_when (initial_school_id=="S11" & final_school_id=="S11" ~ "VIRTUAL",
                               initial_school_id=="S11" & final_school_id %in% c("S01","S02","S03","S04","S05","S06","S07","S08","S09","S10") ~"VIRTUAL_INPERSON",
                               initial_school_id %in% c("S01","S02","S03","S04","S05","S06","S07","S08","S09","S10") & final_school_id=="S11" ~ "INPERSON_VIRTUAL",
                               initial_school_id %in% c("S01","S02","S03","S04","S05","S06","S07","S08","S09","S10") & final_school_id %in% c("S01","S02","S03","S04","S05","S06","S07","S08","S09","S10") ~ "INPERSON"))
```



### Creating dummy variables 
```{r}
# condition assignment 
df$FH2T <- ifelse(df$condition_assignment == 'FH2T', 1, 0)
df$DragonBox <- ifelse(df$condition_assignment == 'DragonBox', 1, 0)
df$Instant <- ifelse(df$condition_assignment == 'Instant', 1, 0)
df$Delay <- ifelse(df$condition_assignment == 'Delay', 1, 0)

# learning modality 
df$virtual <- ifelse(df$initial_school_id == "S11", 1, 0)

df <- df %>%
  mutate(inperson = case_when (initial_school_id=="S11"  ~ "0",
     initial_school_id %in% 
      c("S01","S02","S03","S04","S05","S06","S07","S08","S09","S10") ~"1"))

# movement 
df$stay_INPERSON <- ifelse(df$movement == 'INPERSON', 1, 0)
df$INP_VIR <- ifelse(df$movement == 'INPERSON_VIRTUAL', 1, 0)
df$stay_VIRTUAL <- ifelse(df$movement == 'VIRTUAL', 1, 0)
df$VIR_INP <- ifelse(df$movement == 'VIRTUAL_INPERSON', 1, 0)

# gender
df$FEMALE <- ifelse(df$Gender == 'F', 1, 0)
df$MALE <- ifelse(df$Gender == 'M', 1, 0)

```


```{r}
df <- df %>% select(-"LevelTested", -score)

names(df)[names(df) == "ScaleScore"] <- "Scale.Score5"
names(df)[names(df) == "PerformanceLevel"] <- "Performance.Level5"
```


### Adding pseudo IDs
```{r}
# reading in the crosswalk spreadsheets
school_id <- read_excel("Crosswalk_20220201.xlsx", sheet = "Schools")
otherschools_ID <- read_excel("Crosswalk_20220201.xlsx", sheet = "OtherSchools")
teachers_id <- read_excel("Crosswalk_20220201.xlsx", sheet = "Teachers")
classes_id <- read_excel("Crosswalk_20220201.xlsx", sheet = "Classes")
sections_id <- read_excel("Crosswalk_20220201.xlsx", sheet = "Sections")
students_id <- read_excel("Crosswalk_20220201.xlsx", sheet = "Students")

# adding pseudo School ID
df <- merge(df, school_id, by.x=c("initial_school_id"), by.y=c("Original_School"),  
            all.x=TRUE)
df <- merge(df, school_id, by.x=c("final_school_id"), by.y=c("Original_School"),
            all.x=TRUE)

df <- df %>% rename(initial_SchID = SchID.x,
                    final_SchID = SchID.y)

# adding pseudo other-Schools ID
df <- merge(df, otherschools_ID, by.x=c("G5SCHOOL"), by.y=c("OtherSchool"),  
            all.x=TRUE)
df <- merge(df, otherschools_ID, by.x=c("G5SCHOOL2"), by.y=c("OtherSchool"),  
            all.x=TRUE)

df <- df %>% rename(G5SchID = OthSchID.x,
                    G5SchID2 = OthSchID.y)

df <- merge(df, otherschools_ID, by.x=c("G6SCHOOL"), by.y=c("OtherSchool"), all.x=TRUE)
df <- merge(df, otherschools_ID, by.x=c("G6SCHOOL2"), by.y=c("OtherSchool"), all.x=TRUE)

df <- df %>% rename(G6SchID = OthSchID.x,
                    G6SchID2 = OthSchID.y)

# adding pseudo-teachers ID
df <- merge(df, teachers_id, by.x=c("initial_teacher_id"), by.y=c("Original_Teacher"),  
            all.x=TRUE)
df <- merge(df, teachers_id, by.x=c("final_teacher_id"), by.y=c("Original_Teacher"),
            all.x=TRUE)
 
df <- df %>% rename(initial_TeaID_within_school = TeaID_within_school.x,
                    initial_TeaID= TeaID.x,
                    final_TeaID_within_school = TeaID_within_school.y,
                    final_TeaID = TeaID.y)

# adding pseudo class ID
df <- merge(df, classes_id, by.x=c("initial_teacher_class"), by.y=c("Original_Class"),  
            all.x=TRUE)
df <- merge(df, classes_id, by.x=c("final_teacher_class"), by.y=c("Original_Class"),
            all.x=TRUE)

df <- df %>% rename(initial_ClaID = ClaID.x,
                    final_ClaID= ClaID.y)

# adding section ID
df <- merge(df, sections_id, by.x=c("initial_section_number"), by.y=c("Original_Section"),  
            all.x=TRUE)
df <- merge(df, sections_id, by.x=c("final_section_number"), by.y=c("Original_Section"),  
            all.x=TRUE)

df <- df %>% rename(initial_SecID = SecID.x,
                    final_SecID= SecID.y)

# adding the student IDs
students_id <- students_id %>% select (-student_id) 
df <- merge(df, students_id, by.x=c("student_number"), by.y=c("STUDID"),  
            all.x=TRUE)

# replacing NAs with -999
df <- df %>% replace_na(replace = list(initial_SchID = -999,
                                       final_SchID = -999,
                                       initial_TeaID = -999,
                                       final_TeaID = -999,
                                       initial_ClaID = -999,
                                       final_ClaID = -999))
```


### Removing Original IDs for external use 
```{r}
df <- df %>% select(-student_number, -student_id, -initial_school_id, -final_school_id,
                    -initial_teacher_id, -final_teacher_id, -initial_teacher_class, -final_teacher_class, -initial_section_number, -final_section_number, -G5SCHOOL, -G5SCHOOL2, -G6SCHOOL, -G6SCHOOL2) 
```


```{r}
# reordering
df <- df %>% relocate(StuID,                                   
                      initial_SchID, final_SchID, 
                      initial_TeaID,                         
                      initial_TeaID_within_school, final_TeaID, 
                      final_TeaID_within_school, initial_ClaID,                        
                      final_ClaID,  
                      initial_SecID, final_SecID)


df <- df %>% relocate(c("FH2T", "DragonBox", "Instant", "Delay"), .after = condition_assignment)

df <- df %>% relocate(c("inperson", "virtual", "movement", "stay_INPERSON","stay_VIRTUAL", "INP_VIR", "VIR_INP"), .after = final_SecID)


df <- df %>% relocate(c("FEMALE", "MALE"), .after = Gender)


df <- df %>% relocate(c("Scale.Score7",
                        "Performance.Level7"), .after = Performance.Level5)

df <- df %>% relocate(c("rdm_condition", "condition_assignment"), .after = StuID)

df <- df %>% relocate(raceEthnicityFed, .before=hispanicEthnicity)
df <- df %>% relocate(KEEP, .after = courseName)


df <- df %>% relocate(c(G5SchID, G5SchID2, G5SCHOOL3, G6SchID,G6SchID2, G6SCHOOL3), .after = SST)
```



### data export
```{r}
write_xlsx(x = df, 
           path = "roster_demographic_2022_06_29_N=4,343.xlsx", col_names = TRUE)
```

